An IFS study of Low-powered Radio Galaxies

### 2018-11-10 paper.tex
Minor alteration to the paper
On branch master
 Changes to be committed:
	modified:   paper.tex

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. Warren et al.]{
Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
Martin Bureau,$^{1}$
Bernd Hasemann,$^{2}$
Isabella Prandoni,$^{3}$ \newauthor
Francesco Santoro,$^{3}$
Robert Laing,$^{3}$
Paola Parma,$^{3}$
Hans de Ruiter$^{3}$
and \newauthor
Arturo Mignano$^{3}$
\\
$^{1}$Sub-department of Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK\\
$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. München, Germany\\
$^{3}$INAF - Istituto di Radioastronomia, Via P. Gobetti 101, 40129 Bologna, Italy}

@@

% Abstract of the paper
\begin{abstract}
The most powerful radio galaxies are well studied with a strong consensus in the literature regarding their formations processes. However they are intrinsically rare objects and not representative of the general population of radio galaxies. Low-powered radio galaxies are comparatively poorly studied with many conflicting viewpoints regarding their origin and the extent of the effect of feedback from them.

We present a complete sample of 11 nearby low-powered radio galaxies, observed with a suite of instruments. This paper focuses on the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from optical IFS observations%, while other observation such as \ce{^{12}CO(2-1)} from Atacama Large Millimetre/sub-millimetre Array (ALMA) and radio continuum from the Very Large Array (VLA) will be presented in future papers
. We compare the characteristics and properties of our sample to those of ordinary (i.e.\ optically-selected) ETGs using the Atlas$^\text{3D}$ and MASSIVE IFS surveys. These include the fast/slow rotator classification fraction, kinematic substructures, absorption line strength radial gradients, general stellar population properties, ionized gas distribution and kinematics and the dominant source of ionizing photons.

We tentatively find that our radio-selected ETGs contain a higher mass in of ionized gas than expected, but after accounting for the differences in the mass distribution, we find no further differences between the two samples in the characteristics that can be studied with optical IFU data. We suggest that this is consistent with the notion that low-powered radio galaxies are ordinary ETGs experiencing a brief active phase which maintains their low star-formation rates (also known as maintenance or jet-mode AGN). 
\end{abstract}

@@

	There is a strong consensus within the scientific literature that the most powerful radio galaxies are the result of gas-rich, major mergers causing large amounts of material to fall on to the black hole at the centre of the resulting galaxy, thus producing an immensely powerful AGN which includes a powerful radio jet \citep[e.g.][]{Malin1983, Quillen1992, Lim2000}. However, such galaxies are extremely rare and are not representative of the general radio galaxy population. Most radio galaxies are low-powered, and their basic properties and origins are poorly constrained. One of the most popular suggestions is that they are bona-fide detections of jet-mode AGN.%, a class of AGN thought to maintain the dearth of star formation in early-type galaxies (ETGs), after most of the fuel for star formation has been removed by an earlier event. 
	These radio galaxies are known to be dusty with dust lanes having a tendency to be perpendicular to the jets \citep[e.g.][]{DeRuiter2002, VerdoesKleijn2005}. They have little ionized gas in the ISM \citep[e.g.][]{Sarzi2005}, but often have significant quantities of hot X-ray gas (e.g. \citealt{Canizares1987}; the cold phase of the ISM of radio galaxies will be examined in Ruffa et.al.\ in prep.). If the low star-formation rates typically seen in massive ETGs are preserved by jet-mode AGN, then all such ETGs must regularly go through similar active phases, and therefore low-powered radio galaxies should be much the same as their radio-quiet (quiescent phase) ETG counterparts.

	To test this hypothesis, a complete sample of 11 nearby low-powered radio galaxies was constructed \citet{Prandoni2010} and observed with a suite of instruments. Here, we present the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from integral-field spectroscopic (IFS) observations with the Visible Multi-object Spectrograph (VIMOS) and archival data from the Multi-unit Spectroscopic Explorer (MUSE), both on the Very Large Telescope (VLT). We compare the characteristics and properties (accessible with $V$-band IFS data) of our sample of low-power radio galaxies to those of ordinary (i.e.\ optically-selected) ETGs from the Atlas$^\text{3D}$ and MASSIVE IFS surveys. We hereafter refer to the combined Atlas$^\text{3D}$ and MASSIVE sample as the A+M sample.

	In Section \ref{sec:samp} we, set out the compete sample with our observations and data-reduction methods detailed in Section \ref{sec:obs}. Our data-analysis methods and routines are detailed in Section \ref{sec:analysis} (the maps of our sample produced with these methods are shown in Appendix \ref{sec:maps}). We present our findings regarding the stellar kinematics, absorption line strengths, stellar populations, ionized gas (distribution, kinematics and ionization) in Sections \ref{sec:StarKine}-\ref{sec:gas}, respectively. Finally, we discuss our results and conclude in Section \ref{sec:discuss}.

@@

\section{Data Analysis}
	\label{sec:analysis}
	Both VIMOS and MUSE datasets are spatially binned using Voronoi binning\footnote{http://www-astro.physics.ox.ac.uk/~mxc/software/} \citep{Cappellari2003} and from this point on are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N). For our purposes, we define the `signal' and `noise' of each spaxel as the median value of its spectrum and noise spectrum, respectively. We require a S/N of 30 for all VIMOS datacubes and 50 for the IC 1459 and IC 4296 MUSE datacubes. The NGC 1316 and NGC 1399 MUSE datacubes were binned to a S/N of 50 for the analysis of the stellar kinematics and 100 for the analysis of the emission line kinematics and stellar populations.

@@

	\subsection{Stellar Kinematics}
		\label{subsec:starKin}
		Each bin is fit independently, again using \textsc{pPXF} with the MILES library. For the fit, regions around potential emission lines (listed in Section \ref{subsec:EmissionLines}) are masked, and a fourth order polynomial additive continuum correction is used. The residuals between the best-fitting spectrum and the input spectrum are smoothed in wavelength using a weighted, moving average. This is then summed in quadrature with the noise spectrum (as propagated through the data reduction pipeline) to produce a combined `residual noise' spectrum. A Monte--Carlo (MC) method is used to propagate this residual noise to give to give the quoted uncertainties.

@@

		\subsubsection{Correcting for Stellar Velocity Dispersion}
			\label{subsubsec:EmissionFit}
			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption are outside of the central bandpasses. To do this, we create a stellar best-fitting spectrum which is \textit{not} convolved with the best-fitting LOSVD. Note that for NGC 1316, indices at wavelengths longer than 5800 \AA\ are calculated using the extrapolated best-fitting \textit{pPXF} fit. A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
			\begin{equation}
				I^\text{corr} \equiv \frac{I^\text{unc}}{I^\text{conv}} I^\text{obs} \, .
			\end{equation}
			These corrected indices are those reported and discussed in the sections below.

@@

	\subsection{Other Parameters}
		\subsubsection{Ellipticity}
			\label{subsubsec:ellip}
			In this paper, ellipticity is that of the best-fitting ellipse to the surface-brightness map with an mean radius $R_\text{m}$, of 1 effective radius $R_\text{e}$. % Firstly the centre of the galaxy is found as the luminosity weighted centre using the \textsc{python} routine \textsc{find\_galaxy}, which is part of the \textsc{mge} package\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/} by \citet{Cappellari2002}. 
			as found by the \textsc{idl} routine \textsc{kinemetry}\footnote{http://davor.krajnovic.org/idl/} by \citet{Krajnovic2006}, which finds the best-fitting ellipses at a range of evenly spaced semi-major axes. %This is achieved by performing harmonic expansion of maps along ellipses with a given semi-major axis and, when used for even moments (e.g.\ surface brightness, velocity dispersion, h$_4$ etc.), minimizing the amplitude of the first and second harmonics. 
			The results include the ellipticity, $\epsilon$ and position angle, $PA_\text{phot}$ of the best-fitting ellipse for each semi-major axis. The fit is repeated for increasing semi-major axis until $<$75\% of the ellipse is not contained within the field of view.

@@

\section{Stellar Kinematics}
	\label{sec:StarKine}
	Using the methods above, we produce stellar kinematic maps for all datacubes (shown in Section \ref{sec:maps}). Here, we use these maps to classify each galaxy according to the Atlas$^\text{3D}$ regular/non-regular rotator and fast/slow rotator classification schemes of \citet{Krajnovic2006} and \citet{Cappellari2016}, respectively, as well as the qualitative kinematic classes of \citet{Krajnovic2011}. We use the criteria described in the referenced literature for each of these classification, with the results shown in Table \ref{tab:classify}.

@@

	\subsection{Regular/Non-regular Rotators}
		\label{subsec:RR}
		We find 4/11, or $(36\pm15)$\%, of our sample galaxies are regular rotators. This compares to 82\% of the Atlas$^\text{3D}$ sample being classified as regular rotators \citep{Krajnovic2011}. However the likelihood of a given galaxy being a regular rotator is highly mass dependent with the likelihood decreasing with increasing mass. Thus since our Southern sample are all extremely massive galaxies, we expect to find a higher fraction of non-regular rotators than the Atlas$^\text{3D}$ survey.

@@

		5 out of 11 galaxies, or $(45\pm13)$\%, are slow rotators. This is between that of the Atlas$^\text{3D}$ and MASSIVE projects, who find 13.1\% and 77.5\% of their respective sample galaxies to be slow rotators. As in the regular/non-regular rotators classification scheme (Section \ref{subsec:RR}), slow rotators are more likely to be found in higher mass galaxies and the three samples (Atlas$^\text{3D}$, MASSIVE and our Southern sample) have very different mass distributions (see upper panel of Fig.\,\ref{fig:SRmassFraction}).

		In order to account for the difference in mass distribution, we find the expected fraction of slow rotators in the Southern sample, $f'$, corrected to the mass distribution of the A+M sample, as
		\begin{equation}
			f' = \frac{\sum_{i=0}^N N^\mathrm{SS}_i f^\mathrm{AM}_i}{\sum_{i=0}^N N^\mathrm{SS}} \, , 
		\end{equation}
		where $N^\text{SS}_i$ is the number of Southern sample galaxies in the $i^\text{th}$ mass bin, $N^\text{AM}_i$ is the fraction of slow rotators in the $i^\text{th}$ mass bin in the A+M sample and $N$ is the total number of mass bins. In our case we use the $K$-band absolute magnitude ($M_K$) as a proxy for stellar mass, with bins of 0.5 mag. This gives an expected fraction of $f' = 0.64 \pm 0.06$, just consistent with our finding of $(45\pm13)$\% of the Southern sample galaxies being slow rotators. Again the large uncertainty reflects the low number statistics of the Southern sample. There is, therefore, no discernible difference in the fraction of galaxies that are slow-rotators between our radio-selected Southern sample and the optically-selected A+M sample, once differences in the mass distributions are taken into account.

@@

	\subsection{Kinematic Features}
		We attempt to identify the kinematic features defined by \citet{Krajnovic2011} in an algorithmic way. However, the artefacts from the VIMOS quadrants confuse ellipse fitting algorithms so only maps derived from the MUSE data are classified in this way; kinematic features in maps derived from the VIMOS data are identified by eye. These classification are listed in Col.\,7 of Table \ref{tab:classify} and the corresponding kinematic group to which a given galaxy belongs to is given is Col.\,8. We observe 3 KDCs (although PKS 718-34 is only a tentative classification) such that $29\pm19$\% of non-regular rotators in our Southern sample definitely (not including PKS 718-34) contain KDCs (or $43\pm19$\% including PKS 718-34), with the large uncertainty reflecting the low-number statistics. This is consistent with the Atlas$^\text{3D}$ survey who found find $25\pm7$\% of non-regular rotators host KDCs \citep{Krajnovic2011}.

	\subsection{Intrinsic Shape}
		The misalignment angle, $\Gamma_\text{kin}$, between the photometric and kinematic position angle is given in Col.\,4 of Table \ref{tab:classify}. Intrinsically misaligned systems may appear aligned in certain projections, but aligned systems will be aligned in all projections, and therefore a low value of $\Gamma_\text{kin}$ cannot be used to describe the intrinsic shape of an individual galaxy, but they can be interpreted within a statistical framework as in \citet{Cappellari2007}. However, a high value of $\Gamma_\text{kin}$ can give an insight into the intrinsic shape of an individual galaxy. We find all the regular rotators in our Southern sample, are consistent with having aligned photometry and kinematic position angles to within 11\degr, while non-regular rotators have a large range of values of $\Gamma_\text{kin}$. IC 1531, NGC7075 and PKS 718-34 all have very large uncertainties in the value of $PA_\text{phot}$ due to the VIMOS quadrant artefacts causing the fitting routine of \textsc{kinemetry} to become unreliable.

		The lack of misalignments in regular rotators is consistent with \citet{Cappellari2007}, \citet{Krajnovic2011} and \citet{Fogarty2015}, who all showed that regular rotators almost always have aligned photometric and kinematic axes with very little scatter and that regular rotators with a significant misalignment are either interacting or strongly barred. The lack of misalignments suggests that the regular rotators (including those within our Southern sample) are consistent with being axisymmetric \citep{Cappellari2016}.

@@

\section{Absorption Line Strengths}
	\label{sec:absorption}
	Using the methods described in Section \ref{subsec:absorption} we produce maps of the absorption line strength indices for each galaxy (shown in Appendix \ref{sec:maps}). Here we measure the Mg\,--\,velocity dispersion relation and compare our absorption line strength measurements to the literature.

	\subsection{Mg\,--\,$\sigma$ relation}
		\label{subsec:Mgsigma}
		The Mg$_2$ absorption line index of \citet{Trager1998} has overlapping bandpasses with the Mg\,b index (also of \citeauthor{Trager1998}), but includes the MgH molecular absorption line, and is hence considered a molecular index and is measured in units of magnitude. \citet{Bender1993} observed the tight relationship between the global Mg$_2$ absorption line strength and logarithm of the central velocity dispersion, $\sigma_0$, in elliptical galaxies. They also noticed that residuals to the best-fitting line appeared to be intrinsic as they have a near Gaussian distribution about the median values and do not seem to be correlated to any other galaxy property.

		Part of the red continuum band of the Mg$_2$ index is outside of the spectral range of VIMOS, but \citet{Ziegler1997} show there is an approximately linear relationship between Mg\,b and Mg$_2$, with a gradient of 14.3--15.5\,mag\,\AA$^{-1}$\ depending on metallicity. We thus use Mg\,b as a proxy for Mg$_2$.

		Using an aperture with a radius of 2\arcsec\ on each datacube, we measure $\sigma_0$ and Mg\,b at a spectral resolution of 8.4\,\AA\ full-width half-maximum (FWHM), chosen such that the transformation functions of \citet{Vazdekis2010} can be used to change the literature measurements from the Lick/IDS system to the LIS. The results are shown in Fig.\,\ref{fig:globalMg} with the best-fitting linear relationship (found using \textsc{lts\_linefit} %\footnotemark[\ref{Cappellari}]
		by \citealt{Cappellari2013}) shown by the solid black line. This has a gradient of $3.3 \pm 1.0 \,\mathrm{\text{\AA}\,dex^{-1}}$. It was noticed that NGC 1316 is a possible outlier. Removing NGC 1316 from the fit gives a gradient of $2.5 \pm 0.7 \,\mathrm{\AA\,dex^{-1}}$ (green dashed line in Fig.\,\ref{fig:globalMg}). Both fits are in very good agreement with the gradient found by \citet{Ziegler1997} for a sample of elliptical galaxies within Virgo and Coma using data from \citet{Dressler1987} of $2.5\,\mathrm{\text{\AA}\,dex^{-1}}$ (blue dotted line in Fig.\,\ref{fig:globalMg}), with an intrinsic scatter of 0.16\,\AA\ for galaxies with $\log \sigma_0 \geqslant 2.3$\,dex.

		\begin{figure}
			\includegraphics[width=\columnwidth]{Mg_sigma.png}
			\caption[Global Mg\,b\,--\,$\sigma$]{The Mg\,b\,--\,velocity dispersion relation using a 2\arcsec aperture. We find a similar gradient to our best-fitting (solid black) line as that found by \citet[; blue dotted line]{Ziegler1997}, while removing NGC 1316 from the fit (green dashed) results in an extremely good agreement with \citet{Ziegler1997}.}
			\label{fig:globalMg}
		\end{figure}

@@

			\begin{figure}
				\centering
				\includegraphics[width=\columnwidth]{Hbeta_profile.png}
				\caption{H$\beta$ flux radial profiles derived from the VIMOS datacubes. Solid red lines show $F(\mathrm{H\beta}) \propto r^{-2}$ convolved with a Gaussian function of width equal to the mean seeing (see Table \ref{tab:observations}). This accounts for the PSF of the observations. \label{fig:Hb_profile_VIMOS}}
			\end{figure}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. Warren et al.]{
Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:warrenj@gmx.com}{warrenj@gmx.com}}
%Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
Martin Bureau,$^{1}$
Bernd Hasemann,$^{2}$
Isabella Prandoni,$^{3}$ \newauthor
Francesco Santoro,$^{3}$
Robert Laing,$^{3}$
Paola Parma,$^{3}$
Hans de Ruiter$^{3}$
and \newauthor
Arturo Mignano$^{3}$
\\
$^{1}$Sub-department of Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK\\
$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. München, Germany\\
$^{3}$INAF - Istituto di Radioastronomia, Via P. Gobetti 101, 40129 Bologna, Italy}

@@

% Abstract of the paper
\begin{abstract}
The most powerful radio galaxies are well studied with a strong consensus in the literature regarding their formations processes. However, they are intrinsically rare objects and not representative of the general population of radio galaxies. Low-powered radio galaxies are comparatively poorly studied with many conflicting viewpoints regarding their origin and the extent of the effect of feedback from them.

We present a complete sample of 11 nearby low-powered radio galaxies, observed with a suite of instruments. This paper focuses on the spatially-resolved stellar kinematics and populations, and ionized gas distribution, kinematics and ionization derived from optical IFS observations%, while other observation such as \ce{^{12}CO(2-1)} from Atacama Large Millimetre/sub-millimetre Array (ALMA) and radio continuum from the Very Large Array (VLA) will be presented in future papers
. We compare the characteristics and properties of our sample to those of ordinary (i.e.\ optically-selected) ETGs using the Atlas$^\text{3D}$ and MASSIVE IFS surveys. These include the fast/slow rotator classification fraction, kinematic substructures, absorption line strength radial gradients, general stellar population properties, ionized gas distribution and kinematics and the dominant source of ionizing photons.

We tentatively find that our radio-selected ETGs contain a higher mass in of ionized gas than expected. However, after accounting for the differences in the mass distribution, we find no further differences between the two samples in the characteristics that can be studied with optical IFU data. We suggest that this is consistent with the notion that low-powered radio galaxies are ordinary ETGs experiencing a brief active phase which maintains their low star-formation rates (also known as maintenance or jet-mode AGN). 
\end{abstract}

@@

	There is a strong consensus within the scientific literature that the most powerful radio galaxies are the result of gas-rich, major mergers causing large amounts of material to fall on to the black hole at the centre of the resulting galaxy, thus producing an immensely powerful AGN which includes a powerful radio jet \citep[e.g.][]{Malin1983, Quillen1992, Lim2000}. However, such galaxies are extremely rare and are not representative of the general radio galaxy population. Most radio galaxies are low-powered, and their basic properties and origins are poorly constrained. One of the most popular suggestions is that they are bona-fide detections of jet-mode AGN \citep[e.g.][]{Heckman2014}.%, a class of AGN thought to maintain the dearth of star formation in early-type galaxies (ETGs), after most of the fuel for star formation has been removed by an earlier event. 
	These radio galaxies are known to be dusty with dust lanes having a tendency to be perpendicular to the jets \citep[e.g.][]{DeRuiter2002, VerdoesKleijn2005}. They have little ionized gas in the ISM \citep[e.g.][]{Sarzi2005}, but often have significant quantities of hot X-ray gas (e.g. \citealt{Canizares1987}; the cold phase of the ISM of radio galaxies will be examined in Ruffa et.al.\ in prep.). If the low star-formation rates typically seen in massive ETGs are preserved by jet-mode AGN, then all such ETGs must regularly go through similar active phases, and therefore low-powered radio galaxies should be much the same as their radio-quiet (quiescent phase) ETG counterparts.

	To test this hypothesis, a complete sample of 11 nearby low-powered radio galaxies was constructed by \citet{Prandoni2010} and observed with a suite of instruments. Here, we present the spatially-resolved stellar kinematics and populations, and ionized gas distribution, kinematics and ionization derived from integral-field spectroscopic (IFS) observations with the Visible Multi-object Spectrograph (VIMOS) and archival data from the Multi-unit Spectroscopic Explorer (MUSE), both on the Very Large Telescope (VLT). We compare the characteristics and properties (accessible with $V$-band IFS data) of our sample of low-power radio galaxies to those of ordinary (i.e.\ optically-selected) ETGs from the Atlas$^\text{3D}$ and MASSIVE IFS surveys. We hereafter refer to the combined Atlas$^\text{3D}$ \citep{Cappellari2011} and MASSIVE \citep{Ma2014} sample as the A+M sample.

	In Section \ref{sec:samp} of this paper we set out the compete sample with our observations and data-reduction methods detailed in Section \ref{sec:obs}. Our data-analysis methods and routines are detailed in Section \ref{sec:analysis} (the maps of our sample produced with these methods are shown in Appendix \ref{sec:maps}). We present our findings regarding the stellar kinematics, absorption line strengths, stellar populations, ionized gas (distribution, kinematics and ionization) in Sections \ref{sec:StarKine}-\ref{sec:gas}, respectively. Finally, we discuss our results and conclude in Section \ref{sec:discuss}.

@@

\section{Data Analysis}
	\label{sec:analysis}
	Both VIMOS and MUSE datasets are spatially binned using Voronoi binning\footnote{http://www-astro.physics.ox.ac.uk/~mxc/software/} \citep{Cappellari2003} and from this point on are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N). For our purposes, we define the `signal' and `noise' of each spaxel as the median value of its spectrum and noise spectrum, respectively. We require a S/N of 30 for all VIMOS datacubes and 50 for the IC 1459 and IC 4296 MUSE datacubes. The NGC 1316 and NGC 1399 MUSE datacubes were binned to a S/N of 50 for the analysis of the stellar kinematics and 100 for the analysis of the emission line kinematics and stellar populations. These target S/N were chosen in order to be as low as possible, while still returning meaningful information (as assessed by eye).

@@

	\subsection{Stellar Kinematics}
		\label{subsec:starKin}
		Each bin is fit independently, again using \textsc{pPXF} with the MILES library. For the fit, regions around potential emission lines (listed in Section \ref{subsec:EmissionLines}) are masked, and a fourth order polynomial additive continuum correction is used. The residuals between the best-fitting spectrum and the input spectrum are smoothed in wavelength using a weighted, moving average. This is then summed in quadrature with the noise spectrum (as propagated through the data reduction pipeline) to produce a combined `residual noise' spectrum. A Monte--Carlo (MC) method is used to propagate this residual noise to give to give the quoted uncertainties on all fitted values.

@@

		\subsubsection{Correcting for Stellar Velocity Dispersion}
			\label{subsubsec:EmissionFit}
			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption are outside of the central bandpasses. To do this, we create a stellar best-fitting spectrum which is \textit{not} convolved with the best-fitting LOSVD. Note that for NGC 1316, indices at wavelengths longer than 5800 \AA\ are calculated using the extrapolated best-fitting \textit{pPXF} fit. A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured in the observations ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
			\begin{equation}
				I^\text{corr} \equiv \frac{I^\text{unc}}{I^\text{conv}} I^\text{obs} \, .
			\end{equation}
			These corrected indices are those reported and discussed in the sections below.

@@

	\subsection{Other Parameters}
		\subsubsection{Ellipticity}
			\label{subsubsec:ellip}
			In this paper, ellipticity, $\epsilon$, is that of the best-fitting ellipse to the surface-brightness map with an mean radius $R_\text{m}$, of 1 effective radius $R_\text{e}$. % Firstly the centre of the galaxy is found as the luminosity weighted centre using the \textsc{python} routine \textsc{find\_galaxy}, which is part of the \textsc{mge} package\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/} by \citet{Cappellari2002}. 
			as found by the \textsc{idl} routine \textsc{kinemetry}\footnote{http://davor.krajnovic.org/idl/} by \citet{Krajnovic2006}.%, which finds the best-fitting ellipses at a range of evenly spaced semi-major axes. %This is achieved by performing harmonic expansion of maps along ellipses with a given semi-major axis and, when used for even moments (e.g.\ surface brightness, velocity dispersion, h$_4$ etc.), minimizing the amplitude of the first and second harmonics. 
			The results include the ellipticity, $\epsilon$ and position angle, $PA_\text{phot}$ of the best-fitting ellipse.% for each semi-major axis. The fit is repeated for increasing semi-major axis until $<$75\% of the ellipse is not contained within the field of view.

@@

\section{Stellar Kinematics}
	\label{sec:StarKine}
	Using the methods above, we produce stellar kinematic maps (shown in Appendix \ref{sec:maps}) for all datacubes. Here, we use these maps to classify each galaxy according to the Atlas$^\text{3D}$ regular/non-regular rotator and fast/slow rotator classification schemes of \citet{Krajnovic2006} and \citet{Cappellari2016}, respectively, as well as the qualitative kinematic classes of \citet{Krajnovic2011}. We use the criteria described in the referenced literature for each of these classification, with the results shown in Table \ref{tab:classify}.

@@

	\subsection{Regular/Non-regular Rotators}
		\label{subsec:RR}
		We find 4 out of 11, or $(36\pm15)$\%, of our sample galaxies are regular rotators. This compares to 82\% of the Atlas$^\text{3D}$ sample being classified as regular rotators \citep{Krajnovic2011}. However the likelihood of a given galaxy being a regular rotator is highly mass dependent with the likelihood decreasing with increasing mass. Thus since our Southern sample are all extremely massive galaxies, we expect to find a higher fraction of non-regular rotators than the Atlas$^\text{3D}$ survey.

@@

		5 out of 11 galaxies, or $(45\pm13)$\%, are slow rotators (see Fig.\,\ref{fig:lambdaR_ellip}). This is between that of the Atlas$^\text{3D}$ and MASSIVE projects, who find 13.1\% and 77.5\% of their respective sample galaxies to be slow rotators. As in the regular/non-regular rotators classification scheme (Section \ref{subsec:RR}), slow rotators are more likely to be found in higher mass galaxies and the three samples (Atlas$^\text{3D}$, MASSIVE and our Southern sample) have very different mass distributions (see upper panel of Fig.\,\ref{fig:SRmassFraction}).

		In order to account for the difference in mass distribution, we find the expected fraction of slow rotators in the Southern sample, $f'$, corrected to the mass distribution of the A+M sample, as
		\begin{equation}
			f' = \frac{\sum_{i=0}^N N^\mathrm{SS}_i f^\mathrm{AM}_i}{\sum_{i=0}^N N^\mathrm{SS}} \, , 
		\end{equation}
		where $N^\text{SS}_i$ is the number of Southern sample galaxies in the $i^\text{th}$ mass bin, $N^\text{AM}_i$ is the fraction of slow rotators in the $i^\text{th}$ mass bin in the A+M sample and $N$ is the total number of mass bins. In our case we use the $K$-band absolute magnitude ($M_K$) as a proxy for stellar mass, with bins of 0.5 mag. This gives an expected fraction of $f' = 0.64 \pm 0.06$, which is consistent with our finding of $(45\pm13)$\% of the Southern sample galaxies being slow rotators. Again the large uncertainty reflects the low number statistics of the Southern sample. There is, therefore, no discernible difference in the fraction of galaxies that are slow-rotators between our radio-selected Southern sample and the optically-selected A+M sample, once differences in the mass distributions are taken into account.

@@

	\subsection{Kinematic Features}
		We attempt to identify the kinematic features defined by \citet{Krajnovic2011} in an algorithmic mannor, however, the artefacts from the VIMOS quadrants confuse ellipse fitting algorithms. Due to this, only maps derived from the MUSE data are classified in this way, while kinematic features in maps derived from the VIMOS data are identified by eye. These classification are listed in Col.\,7 of Table \ref{tab:classify} and the corresponding kinematic group \citep[also defined by][]{Krajnovic2011} to which a given galaxy belongs to is given is Col.\,8. We observe 3 KDCs (although PKS 718-34 is only a tentative classification) such that $29\pm19$\% of non-regular rotators in our Southern sample definitely (not including PKS 718-34) contain KDCs (or $43\pm19$\% including PKS 718-34), with the large uncertainty reflecting the low-number statistics. This is consistent with the Atlas$^\text{3D}$ survey who found find $25\pm7$\% of non-regular rotators host KDCs \citep{Krajnovic2011}.

	\subsection{Intrinsic Shape}
		The misalignment angle, $\Gamma_\text{kin}$, between the photometric and kinematic position angle is given in Col.\,4 of Table \ref{tab:classify}. IC 1531, NGC7075 and PKS 718-34 all have very large uncertainties in the value of $PA_\text{phot}$ due to the VIMOS quadrant artefacts causing the fitting routine of \textsc{kinemetry} to become unreliable.

		While intrinsically misaligned systems may appear aligned in certain projections, aligned systems will be aligned in all projections. Therefore a low value of $\Gamma_\text{kin}$ cannot be used to describe the intrinsic shape of an individual galaxy, but can only be interpreted within a statistical framework as in \citet{Cappellari2007}. However, a high value of $\Gamma_\text{kin}$ can give an insight into the intrinsic shape of an individual galaxy. We find all the regular rotators in our Southern sample, are consistent with having aligned photometry and kinematic position angles to within 11\degr, while non-regular rotators have a large range of values of $\Gamma_\text{kin}$.

		The lack of misalignments in regular rotators is consistent with \citet{Cappellari2007}, \citet{Krajnovic2011} and \citet{Fogarty2015}, who all show that regular rotators almost always have aligned photometric and kinematic axes with very little scatter. They also point out that regular rotators with a significant misalignment tend to be either interacting or strongly barred. The lack of misalignments suggests that the regular rotators (including those within our Southern sample) are consistent with being axisymmetric \citep{Cappellari2016}.

@@

\section{Absorption Line Strengths}
	\label{sec:absorption}
	Using the methods described in Section \ref{subsec:absorption}, we produce maps of the absorption line strength indices for each galaxy (shown in Appendix \ref{sec:maps}). In this section, we measure the Mg\,--\,velocity dispersion relation and compare our absorption line strength measurements to the literature.

	\subsection{Mg\,--\,$\sigma$ relation}
		\label{subsec:Mgsigma}
		%The Mg$_2$ absorption line index of \citet{Trager1998} has overlapping bandpasses with the Mg\,b index (also of \citeauthor{Trager1998}), but includes the MgH molecular absorption line, and is hence considered a molecular index and is measured in units of magnitude. 
		\citet{Bender1993} observed the tight relationship between the global Mg$_2$ absorption line strength and logarithm of the central velocity dispersion, $\sigma_0$, in elliptical galaxies. They also noticed that residuals to the best-fitting line appeared to be intrinsic as they have a near Gaussian distribution about the median values and do not seem to be correlated to any other galaxy property.

		Part of the red continuum band of the Mg$_2$ index is outside of the spectral range of VIMOS, but \citet{Ziegler1997} show there is an approximately linear relationship between Mg\,b and Mg$_2$, with a gradient of 14.3--15.5\,mag\,\AA$^{-1}$\ depending on metallicity. Thus, following \citet{Ziegler1997}, we also use Mg\,b as a proxy for Mg$_2$.

		Using an aperture with a radius of 2\arcsec\ on each datacube, we measure $\sigma_0$ and Mg\,b at a spectral resolution of 8.4\,\AA\ full-width half-maximum (FWHM), chosen such that the transformation functions of \citet{Vazdekis2010} can be used to change the literature measurements from the Lick/IDS system to the LIS. The results are shown in Fig.\,\ref{fig:globalMg} with the best-fitting linear relationship %(found using \textsc{lts\_linefit} %\footnotemark[\ref{Cappellari}]
		%by \citealt{Cappellari2013}) 
		shown by the solid black line. This has a gradient of $3.3 \pm 1.0 \,\mathrm{\text{\AA}\,dex^{-1}}$. It was noted that NGC 1316 is a possible outlier. Removing NGC 1316 from the fit gives a gradient of $2.5 \pm 0.7 \,\mathrm{\AA\,dex^{-1}}$ (green dashed line in Fig.\,\ref{fig:globalMg}). Both fits are in very good agreement with the gradient found by \citet{Ziegler1997} (transformed to the LIS system using the functions of \citealt{Vazdekis2010}) for a sample of elliptical galaxies within Virgo and Coma %using data from \citet{Dressler1987} 
		of $2.7\,\mathrm{\text{\AA}\,dex^{-1}}$ (blue dotted line in Fig.\,\ref{fig:globalMg}).%, with an intrinsic scatter of 0.16\,\AA\ for galaxies with $\log \sigma_0 \geqslant 2.3$\,dex.

		\begin{figure}
			\includegraphics[width=\columnwidth]{Mg_sigma.png}
			\caption[Global Mg\,b\,--\,$\sigma$]{The Mg\,b\,--\,velocity dispersion relation using a 2\arcsec aperture. We find a similar gradient to our best-fitting (solid black) line as that found by \citet[transformed to LIS with the functions of \citealt{Vazdekis2010}; blue dotted line]{Ziegler1997}. Removing NGC 1316 from the fit (green dashed) results in an extremely good agreement with \citet{Ziegler1997}.}
			\label{fig:globalMg}
		\end{figure}

@@

			\begin{figure}
				\centering
				\includegraphics[width=\columnwidth]{Hbeta_profile.png}
				\caption{H$\beta$ flux radial profiles derived from the VIMOS datacubes. Solid red lines show $F(\mathrm{H\beta}) \propto r^{-2}$ convolved with a Gaussian function of width equal to the mean seeing taken from the observation logs. This accounts for the PSF of the observations. \label{fig:Hb_profile_VIMOS}}
			\end{figure}
